\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-18 methodology.tex
some update in section 4

The component under test, the real ExtMgr in vNext, is wrapped inside the \texttt{ExtentManager} \psharp machine in the testing harness.

@@

%Using method dispatch for modeling is straightforward. The system under test exposes a set of APIs as \emph{virtual methods}. The developer can then \emph{override} these APIs and replace them with \emph{mocks} that will execute instead of the original implementations during systematic testing with \psharp.

%\begin{figure}[t]
%\begin{lstlisting}
%// Public interface of the real network engine
%class NetworkEngine {
  %public virtual void SendMessage(Socket s, Message msg);
  %public virtual void EnqueueMessage(Message msg);
%}
%
%// The mocked network engine used during testing
%class MockedNetEngine : NetworkEngine {
  %ExtentManager EM; // Handle to actual system under test
  %MachineId Env; // Handle to modeled environment
  %
  %public MockedNetEngine(ExtentManager em, MachineId env) {
    %this.EM = em;
    %this.Env = env;
  %}
  %
  %public override void SendMessage(Socket s, Message msg) {
    %PSharpRuntime.Send(this.Env, new MsgEvent(), s, msg);
  %}
  %
  %public override void EnqueueMessage(Message msg) {
    %this.EM.ProcessMessage(msg);
  %}
%}
%\end{lstlisting}
%\vspace{-2mm}
%\caption{The mocked network engine used for testing the Azure Storage vNext system.}
%\label{fig:enginecode}
%%\vspace{-2mm}
%\end{figure}

@@

  [OnEvent(TimerTick), nameof(ProcessExtentRepair))]
  void ProcessExtentRepair() {
    // extent repair loop driven by external timer
    extMgr.ProcessEvent(new ExtentRepairEvent());
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{Component under test: the real Extent Manager wrapped inside an \texttt{ExtentManager} \psharp machine.}
\label{fig:wrap_target}
%\vspace{-2mm}
\end{figure}

>>>>

The system-under-test, the real ExtMgr in vNext, is wrapped inside the \texttt{ExtentManager} \psharp machine in the testing harness.

@@

%Using method dispatch for modeling is straightforward. The system-under-test exposes a set of APIs as \emph{virtual methods}. The developer can then \emph{override} these APIs and replace them with \emph{mocks} that will execute instead of the original implementations during systematic testing with \psharp.

%\begin{figure}[t]
%\begin{lstlisting}
%// Public interface of the real network engine
%class NetworkEngine {
  %public virtual void SendMessage(Socket s, Message msg);
  %public virtual void EnqueueMessage(Message msg);
%}
%
%// The mocked network engine used during testing
%class MockedNetEngine : NetworkEngine {
  %ExtentManager EM; // Handle to actual system-under-test
  %MachineId Env; // Handle to modeled environment
  %
  %public MockedNetEngine(ExtentManager em, MachineId env) {
    %this.EM = em;
    %this.Env = env;
  %}
  %
  %public override void SendMessage(Socket s, Message msg) {
    %PSharpRuntime.Send(this.Env, new MsgEvent(), s, msg);
  %}
  %
  %public override void EnqueueMessage(Message msg) {
    %this.EM.ProcessMessage(msg);
  %}
%}
%\end{lstlisting}
%\vspace{-2mm}
%\caption{The mocked network engine used for testing the Azure Storage vNext system.}
%\label{fig:enginecode}
%%\vspace{-2mm}
%\end{figure}

@@

  [OnEvent(TimerTick), nameof(ProcessExtentRepair))]
  void ProcessExtentRepair() {
    // extent repair loop driven by external timer
    extMgr.ProcessEvent(new ExtentRepairEvent());
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{System-under-test: instance of the real Extent Manager wrapped inside the \texttt{ExtentManager} machine.}
\label{fig:wrap_target}
%\vspace{-2mm}
\end{figure}
